A Gentle Introduction and Application of Feature-Based Clustering with Psychological Time Series

### 2023-07-29 sections/02InputVariables.Rmd
checkmark

varNames %>%
  filter(
    pca != 0,
    varNam %in% c(varNamS123PCA, varNamS1PCA, varNamS2PCA, varNamS3PCA)
  ) %>%
  mutate(
    contactSpecific = recode(
      .$contactSpecific,
      `-1` = "No Interaction Only",
      `0` = "unspecific",
      `1` = "Interaction Only"
    ),
    study1 = ifelse(!is.na(studyS1), 1, 0),
    study2 = ifelse(!is.na(studyS2), 1, 0),
    study3 = ifelse(!is.na(studyS3), 1, 0)
  ) %>% 
  select(varNam, question, varGroup, contactSpecific, study1, study2, study3) %>%
  filter(study1 == 1 & study2 == 1 & study3 == 1) %>%
  group_by(varGroup, varNam, question, contactSpecific, study1, study2, study3) %>%
  summarise(n = n()) %>%
  pivot_wider(names_from = c("varNam", "question", "varGroup", "study1", "study2", "study3"), values_from = n, names_sep=" - ") %>%
  ungroup %>%
  t %>%
  as.data.frame %>%
  janitor::row_to_names(1) %>%
  replace(is.na(.), 0) %>%
  tibble::rownames_to_column(., var = "variable") %>%
  separate(variable, c("Variable", "Question", "Aspect", "study1", "study2", "study3"), " - ") %>%
  mutate(across(c(study1, study2, study3), as.numeric)) %>%
  select(-study1, -study2, -study3) %>%
  arrange(`Interaction Only`, Variable) %>% 
  mutate(ESM = 1) %>%
  mutate_all(~recode(.x, `0`="", ` 1`="✔")) %>%
  relocate(starts_with("ESM"), .after = "Aspect") %>%
  # relocate(starts_with("study"), .after = last_col()) %>%
  # rename_with(., ~ gsub("study", "Study ", .x, fixed = TRUE)) %>%
  kbl(.,
      escape = FALSE,
      booktabs = T,
      align = c("l", "l", "l", rep("c", ncol(.)-3)),
      digits = 2,
      format = "latex",
      label = "var_selection",
      caption = "Variable Selection") %>%
  add_header_above(c(" " = 4, "Contact Specific" = 2)) %>%
  kable_styling(latex_options = "scale_down") %>%
  gsub("\\begin{table}", "\\begin{sidewaystable*}[!hbtp]\n\\centering", ., fixed = TRUE) %>%
  gsub("\\end{table}", "\\end{sidewaystable*}", ., fixed = TRUE) %>%
  save_kable("tables/var_selection.tex")

>>>>

varNames %>%
  filter(
    pca != 0,
    varNam %in% c(varNamS123PCA, varNamS1PCA, varNamS2PCA, varNamS3PCA)
  ) %>%
  mutate(
    contactSpecific = recode(
      .$contactSpecific,
      `-1` = "No Interaction Only",
      `0` = "unspecific",
      `1` = "Interaction Only"
    ),
    study1 = ifelse(!is.na(studyS1), 1, 0),
    study2 = ifelse(!is.na(studyS2), 1, 0),
    study3 = ifelse(!is.na(studyS3), 1, 0)
  ) %>% 
  select(varNam, question, varGroup, contactSpecific, study1, study2, study3) %>%
  filter(study1 == 1 & study2 == 1 & study3 == 1) %>%
  group_by(varGroup, varNam, question, contactSpecific, study1, study2, study3) %>%
  summarise(n = n()) %>%
  pivot_wider(names_from = c("varNam", "question", "varGroup", "study1", "study2", "study3"), values_from = n, names_sep=" - ") %>%
  ungroup %>%
  t %>%
  as.data.frame %>%
  janitor::row_to_names(1) %>%
  replace(is.na(.), 0) %>%
  tibble::rownames_to_column(., var = "variable") %>%
  separate(variable, c("Variable", "Question", "Aspect", "study1", "study2", "study3"), " - ") %>%
  mutate(across(c(study1, study2, study3), as.numeric)) %>%
  select(-study1, -study2, -study3) %>%
  arrange(`Interaction Only`, Variable) %>% 
  mutate(ESM = 1) %>%
  mutate_all(~recode(.x, `0`="", ` 1`="\\Checkmark")) %>%
  relocate(starts_with("ESM"), .after = "Aspect") %>%
  # relocate(starts_with("study"), .after = last_col()) %>%
  # rename_with(., ~ gsub("study", "Study ", .x, fixed = TRUE)) %>%
  kbl(.,
      escape = FALSE,
      booktabs = T,
      align = c("l", "l", "l", rep("c", ncol(.)-3)),
      digits = 2,
      format = "latex",
      label = "var_selection",
      caption = "Variable Selection") %>%
  add_header_above(c(" " = 4, "Contact Specific" = 2)) %>%
  kable_styling(latex_options = "scale_down") %>%
  gsub("\\begin{table}", "\\begin{sidewaystable*}[!hbtp]\n\\centering", ., fixed = TRUE) %>%
  gsub("\\end{table}", "\\end{sidewaystable*}", ., fixed = TRUE) %>%
  save_kable("tables/var_selection.tex")

### 2023-07-29 tables/var_selection.tex
checkmark

\caption{\label{tab:var_selection}Variable Selection}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lllccc}
\toprule
\multicolumn{4}{c}{ } & \multicolumn{2}{c}{Contact Specific} \\
\cmidrule(l{3pt}r{3pt}){5-6}
Variable & Question & Aspect & ESM & unspecific & Interaction Only\\
\midrule
AttitudesPartner & At the moment, how favorably do you feel towards -NAME- & cognition & ✔ &  & ✔\\
InteractionContextAccidental & The interaction with -NAME- was accidental. & cognition & ✔ &  & ✔\\
InteractionContextCooperative & The interaction with -NAME- was cooperative. & cognition & ✔ &  & ✔\\
InteractionContextRepresentativeNL & The interaction with -NAME- was representative of the Dutch. & cognition & ✔ &  & ✔\\
InteractionContextvoluntary & The interaction with -NAME- was voluntary. & cognition & ✔ &  & ✔\\
\addlinespace
KeyNeedDueToPartner & -NAME- helped fulfill your goal (-GOAL-) & needs & ✔ &  & ✔\\
qualityMeaning & Overall, the interaction with -NAME- was: Superficial --- Meaningful & cognition & ✔ &  & ✔\\
qualityOverall & Overall, the interaction with -NAME- was: Unplesant --- Plesant & cognition & ✔ &  & ✔\\
AttitudesDutch & At the moment, how favorably do you feel towards the Dutch. & cognition & ✔ & ✔ & \\
DaytimeNeedFulfillment & During this -morning/afternoon- your goal (-GOAL-) was fulfilled. & needs & ✔ & ✔ & \\
\addlinespace
KeyNeedFulfillment & During your interaction with -NAME- your goal (-GOAL-) was fulfilled. & needs & ✔ & ✔ & \\
exWB & How do you feel right now? very sad --- very happy & emotion & ✔ & ✔ & \\
\bottomrule
\end{tabular}}
\end{sidewaystable*}

>>>>

\caption{\label{tab:var_selection}Variable Selection}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lllccc}
\toprule
\multicolumn{4}{c}{ } & \multicolumn{2}{c}{Contact Specific} \\
\cmidrule(l{3pt}r{3pt}){5-6}
Variable & Question & Aspect & ESM & unspecific & Interaction Only\\
\midrule
AttitudesPartner & At the moment, how favorably do you feel towards -NAME- & cognition & \Checkmark &  & \Checkmark\\
InteractionContextAccidental & The interaction with -NAME- was accidental. & cognition & \Checkmark &  & \Checkmark\\
InteractionContextCooperative & The interaction with -NAME- was cooperative. & cognition & \Checkmark &  & \Checkmark\\
InteractionContextRepresentativeNL & The interaction with -NAME- was representative of the Dutch. & cognition & \Checkmark &  & \Checkmark\\
InteractionContextvoluntary & The interaction with -NAME- was voluntary. & cognition & \Checkmark &  & \Checkmark\\
\addlinespace
KeyNeedDueToPartner & -NAME- helped fulfill your goal (-GOAL-) & needs & \Checkmark &  & \Checkmark\\
qualityMeaning & Overall, the interaction with -NAME- was: Superficial --- Meaningful & cognition & \Checkmark &  & \Checkmark\\
qualityOverall & Overall, the interaction with -NAME- was: Unplesant --- Plesant & cognition & \Checkmark &  & \Checkmark\\
AttitudesDutch & At the moment, how favorably do you feel towards the Dutch. & cognition & \Checkmark & \Checkmark & \\
DaytimeNeedFulfillment & During this -morning/afternoon- your goal (-GOAL-) was fulfilled. & needs & \Checkmark & \Checkmark & \\
\addlinespace
KeyNeedFulfillment & During your interaction with -NAME- your goal (-GOAL-) was fulfilled. & needs & \Checkmark & \Checkmark & \\
exWB & How do you feel right now? very sad --- very happy & emotion & \Checkmark & \Checkmark & \\
\bottomrule
\end{tabular}}
\end{sidewaystable*}
